FIXME

### 2013-02-10 stackExchange/writeups/iccm-2013/writeup.tex
foo
Former-commit-id: bb4834d7223f2c68e83546109f5d4f36013baf4f [formerly 68cf953e7ac53a7c25f4fabacb204f2ed619bcc0]
Former-commit-id: 5abd299412cbedfe49171f6dc51234ece143b21a

The StackOverflow dataset consists of all questions and answers posted on stackoverflow.com.
The questions are all programming related and can be posted by anyone with an account, which is free to create.
Each question is tagged by the author with (presumably) the tags that are most representative of the post.
Example tags are programming languages (PHP, Common-Lisp, MySQL, C\#) and also general topics (databases, optimization, arrays).
An Example question from the stackoverflow.com site is included in Figure \ref{fig:examplePost}.
Note that the author tagged this post with java, twitter, twitter4j, and twitter−oauth.

\begin{figure}[ht]
  \centering
  \resizebox{\linewidth}{!}{\includegraphics{visPost-4148010-act-cropped.pdf}}
  \caption{Example Post}
  \label{fig:examplePost}
\end{figure}

@@

A formal description of the model's equations are included below:

\begin{table}[!ht]
  \begin{center} 
    \caption{Sample table title.} 
    \label{sample-table} 
    \vskip 0.12in
    \begin{tabular}{ll} 
      \hline
      Common Name &  Equation \\
      \hline
      Activation & 		$A_{i} = B_{i} + \sum_{j\in T}^{ } W_{j} S_{ji} + \sum_{j\in B}^{ } W_{j} S_{ji} - O$ \\
      Base Level & 		$B_{i} = log \frac{p_{i}}{1-p_{i}}$ \\
      Strength Assoc. &		$S_{ji} = log \frac{p(i|j)}{p(i))} = log \frac{p(j,i)}{p(j)p(i)}$ \\
      & 			$= log \frac{NN(j,i)}{N_{Row}(j)N_{Col}(i)}$ \\
      Attentional Weight	& $W_{j} = WE_{j}$ \\
      Scaled Entropy & 		$E_{j} = 1-\frac{H_{j}}{H_{max}}$ \\
      Entropy & 		$H_{j} = -\sum_{i=1}^{N}p(i|j)log\left (  p(i|j) \right )$ \\
      Max Entropy & 		$H_{max} = maxH$ \\
      Offset & 			$O = \frac{1}{5}\sum_{i\in top 5}^{ } A_{i}$ \\
      \hline
    \end{tabular} 
  \end{center} 
\end{table}

@@

\begin{figure}[ht]
  \centering
  \resizebox{\linewidth}{!}{\includegraphics{visPost-4148010-act-cropped.pdf}}
  \caption{
    Model's prediction of top-ten tags for post in Figure \ref{fig:examplePost}.
    The title is the title text of the post.
    The attentional weight (entropy) for each word in the title is included below each word.
    The user-chosen tags are included below the attentional weights.
    The stacked bar graphs are the total activation for the top-ten predicted model tags for the post.
    Each bar graph is partitioned into the 3 model components that vary between tags within a post (not the post offset).
}
  \label{fig:modelPost}
\end{figure}

Note how the base level activation and contextual activation combine to predict tags that are both frequently used and contextually relevant.
For example, note that the 'twitter' tag leverages a combination of contextual activation and prior activation to achieve a high total activation.
Alternatively, the 'twitter-4j' tag relies almost entirely on context to achieve high activation.
And note that the model is by no means perfect.
For example, the 'java' tag was used by the post author, and it does have a high prior activation, but context in this particular post was not associated too highly with java, so the model rank of java suffered.

>>>>

The StackOverflow dataset consists of all questions and answers posted on stackoverflow.com.
The questions are all programming related and can be posted by anyone with an account, which is free to create.
Each question is tagged by the author with (presumably) the tags that are most representative of the post.
Example tags are programming languages (PHP, Common-Lisp, MySQL, C\#) and also general topics (databases, optimization, arrays).
An Example question from the stackoverflow.com site is included in Figure \ref{fig:examplePost}.
Note that the author tagged this post with javascript, firefox, dom, and svg.

\begin{figure}[ht]
  \centering
  \resizebox{\linewidth}{!}{\includegraphics{visPost-2977094-screen-cropped.pdf}}
  \caption{Example Post}
  \label{fig:examplePost}
\end{figure}

@@

A formal description of the model's equations are included in Table \ref{sample-table}.

\renewcommand{\arraystretch}{1.5}% Wider
\renewcommand{\tabcolsep}{.5mm}
\begin{table}[!ht]
  \begin{center} 
    \caption{Sample table title.} 
    \label{sample-table} 
    \vskip 0.12in
    \begin{tabular}{ll} 
      \hline
      Common Name &  Equation \\
      \hline
      Activation & 		$A_{i} = B_{i} + \sum_{j\in T}^{ } W_{j} S_{ji} + \sum_{j\in B}^{ } W_{j} S_{ji} - O$ \\
      Base Level & 		$B_{i} = log \frac{p_{i}}{1-p_{i}}$ \\
      Strength Assoc. &		$S_{ji} = log \frac{p(i|j)}{p(i))} = log \frac{NN(j,i)}{N_{Row}(j)N_{Col}(i)}$ \\
      Attention Weight	& 	$W_{j} = WE_{j}$ \\
      Scaled Entropy & 		$E_{j} = 1-\frac{H_{j}}{H_{max}}$ \\
      Entropy & 		$H_{j} = -\sum_{i=1}^{N}p(i|j)log\left (  p(i|j) \right )$ \\
      Max Entropy & 		$H_{max} = maxH$ \\
      Offset & 			$O = \frac{1}{5}\sum_{i\in top 5}^{ } A_{i}$ \\
      \hline
    \end{tabular} 
  \end{center} 
\end{table}

@@

\begin{figure}[ht]
  \centering
  \resizebox{\linewidth}{!}{\includegraphics{visPost-2977094-act-cropped.pdf}}
  \caption{
    Model's prediction of top-ten tags for post in Figure \ref{fig:examplePost}.
    The title is the title text of the post.
    The attentional weight (entropy) for each word in the title is included below each word.
    The user-chosen tags are included below the attentional weights.
    The stacked bar graphs are the total activation for the top-ten predicted model tags for the post.
    Each bar graph is partitioned into the 3 model components that vary between tags within a post (not the post offset).
}
  \label{fig:modelPost}
\end{figure}

Note how the base level activation and contextual activation combine to predict tags that are both frequently used and contextually relevant.
For example, note that the 'javascript' tag leverages a combination of contextual activation and prior activation to achieve a high total activation.
Alternatively, the 'svg' tag relies almost entirely on context to achieve high activation.
And note that the model is by no means perfect.
For example, note that 'html' is not tagged by the author, but the model ranks it as the second highest tag.
And note that author's tag 'firefox' is only ranked 8th by the model.
